Edge sign prediction in general graphs and Correlation Clustering

### 2017-10-03 troll/conclusions.tex
mark content added from the aistats paper
split the troll conclusion in two parts

\section{Conclusion}

Finally, we study the online adversarial setting, where trollness and (un)trustworthiness naturally
lend themselves to define a notion of edge sign regularity. Based on this regularity, we provide an
upper and an (almost matching) lower bounds on the expected number of prediction mistakes. Before
exploring in the next chapter another learning bias for \esp{}, which is not based on trollness and
(un)trustworthiness, we present directions in which this work could be extended.

\bigskip

Given the fundamental role of our generative model, we would like to adapt it in order to handle
the three problem extensions presented in the related work of \autoref{sec:troll_related}.

@@

>>>>

\section{Open questions}

Given the fundamental role of our generative model, we would like to adapt it in order to handle
the three problem extensions presented in the related works of \autoref{sec:troll_related}.

@@

\section{Summary}

Finally, we study the online adversarial setting, where trollness and (un)trustworthiness naturally
lend themselves to define a notion of edge sign regularity. Based on this regularity, we provide an
upper and an (almost matching) lower bounds on the expected number of prediction mistakes. We
conclude by presenting three directions in which our generative model could be extended: namely
use side information as priors, guide budgeted queries in active learning and generate weights in
addition to signs.

In the next chapter, we will go even further than this generative model and explore another learning
bias for \esp{}, which is not based on trollness and (un)trustworthiness, but rather on the social
balance theory.
